\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-12 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
add news paragraphs until besteffort for result section in subsection Whisper use case

	\begin{enumerate}
	  \item Scientific whisper results: theses, articles, prices
  	  \item Organisation with a DataSet: Evaluation local/Ciment, capacities adaptation students
  	  \item First step: Conversion data format, distributions of datas on ressources: decrease the concurrency
  	  \item Evolution specification, genericty of the codes, degree of automatization
  	  \item Back to the first package signal processing for Japan
  	  \item Identification seismogram: Dates, stations
  	  \item Adding python modules for data retrieve + Calls.
  	  \item Focus on encapsulation queries
  	  \item Modelization distribution: sublist Dates, Stations
      \item The files start.bash and parameters
      \item The jdl file
  	  \item Back to the package correlation: similar adds + possibility hash table
  	  \item Comparison data management, example Japan processing/USArray 
  	  \item Focus on the distribution problem (Space complexity/Transfer)
  	  \item Mode besteffort: increase of datas transfert, it possibly adds also new steps of data storage.
  	  \item Some order of magnitude for the Japan Computation.
  	  \item On the Japanese results.
  	\end{enumerate}

@@

Here we divide the dates in 160 sublists and the stations in 8 sublists. 
The line "traces160\_0\_8\_1 160 0 8 1" correponds to a job named 'traces160\_0\_8\_1' where
we take the sublist of dates of index 0 and the sublist of stations of index 1 (each sublist have the length +/-1).
(There are also other parameters for components and networks not described here.)

@@

  "clusters": {
    "c1": {
       	"prologue": [
       	... lines of codes for the 
       	... cluster c1 first of all ],
       	"project": "whisper",
       	"walltime": "00:20:00"
       	},
    "c2": {
    	"prologue": [
        ... lines of codes for the 
        ... cluster c2 first of all ],
        "project": "whisper",
        "max_jobs": "450",
        "walltime": "00:30:00"
    	},
    ...
    }
...
}
\end{lstlisting}

Here the campaign named 'test\_processing' take only one core. It run the file 'start.bash' with the parameter
file 'param.txt' in mode besteffort. It uses the clusters named 'c1' and 'c2' for the project 'whisper' with the duration
defined by 'walltime'. We can add other parameters for each clusters such that the maximum number of
jobs runing at the same time (the variable 'max\_jobs').

>>>>

	\begin{enumerate}
	  \item Scientific whisper results: theses, articles, prices
  	  \item Organisation with a DataSet: Evaluation local/Ciment, capacities adaptation students
  	  \item Comparison data management, example Japan processing/USArray 
  	  \item Evolution specification, genericty of the codes, degree of automatization
  	  \item First step: Conversion data format, distributions of datas on ressources: decrease the concurrency
  	  \item Back to the first package signal processing for Japan
  	  \item Identification seismogram: Dates, stations  / Modelization distribution: sublist Dates, Stations
  	  \item Adding python modules for data retrieve + Calls.
  	  \item Focus on encapsulation queries
      \item The file parameters
      \item the file start.bash
      \item The jdl file
  	  \item Back to the package correlation: similar adds 
  	  \item Focus on the distribution problem (Space complexity/Transfer)
  	  \item Mode besteffort: increase of datas transfert, it possibly adds also new steps of data storage.
  	  \item Some order of magnitude for the Japan Computation.
  	  \item On the Japanese results.
  	\end{enumerate}

@@

Here we divide the dates in 160 sublists and the stations in 8 sublists. 
The line "traces160\_0\_8\_1 160 0 8 1" correponds to a job named 'traces160\_0\_8\_1' where
we take the sublist of dates of index 0 and the sublist of stations of index 1 (each sublist have the same length +/-1).
(There are also other parameters for components and networks not described here.)

@@

  "clusters": {
    "c1": {
       	"prologue": [
       	secure_iget -f /IrodsColl/start.bash,
       	secure_iget -f /IrodsColl/param.txt,
       	... other lines of commands ],
       	"project": "whisper",
       	"walltime": "00:20:00"
       	},
    "c2": {
    	"prologue": [
        ... lines of commands ],
        "project": "whisper",
        "max_jobs": "450",
        "walltime": "00:30:00"
    	},
    ...
    }
...
}
\end{lstlisting}

Here the campaign named 'test\_processing' take only one core. It run the file 'start.bash' with the parameter
file 'param.txt' in mode besteffort. It uses the clusters named 'c1' and 'c2' for the project 'whisper' with the duration
defined by 'walltime'. In the prologue, we retrieve script and the parameter file on iRODS. 
One can add other parameters for each clusters such that the maximum number of
jobs runing at the same time (the variable 'max\_jobs').

Concerning the package for the correlations (the second part of the figure \ref{whisperGeneralWorflow}), we also add similar modules
to retrieve on iRods the subsets of seismograms that have been treated. In order to compute all the correlations that corresponds to
all the couple of seismograms we have two types of processes. For a fix subset of dates, either we retrieve one subset of stations 
and compute all the existing couples for this subset, or either we retrieve two disjoint subsets of stations and compute all the 
correlations where each seismogram is in a different sublist. This distribution for the computation of the correlations offers a good granularity.

With this kind of distribution for the stations, the transfer bewteen iRODS and the computational node becomes proportional to 
the distribution, i.e. the number of sublists of stations. Therefore we have to maximize the distribution of the dates and minimize it
for the stations in order to obtain a reasonable walltime. Note that it is possible to improve the transfert.
However, a fairly simple improvement have to effect that the distribution become dependent on the distributed architecture of computation.
In order to keep genericity of the codes we do not change this aspect.

The mode besteffort also increase the transfert of data because some job are killed and submit in an other place.
Moreover in some cases, such that a big walltime, we add new steps of iRODS storage for the process in order to store intermediate calculation
(It is not the case for correlation because of the good granularity). 
Note that this may represent a significant development effort.
